Untitled

### 2020-12-21 ms/manuscript.Rmd
Migrate from drake to targets

```{r load-data}
loadd(
  list = c(
    "climate",
    "filmy_species",
    "moorea_sites",
    "phylosig",
    "range_types",
    "combined_species_means",
    "t_test_results",
    "env_range_dt_model_summary"
  )
)
```

@@

# Make helper function to check on p-value significance and extract from t_test_results
#
#' @param species_select Name of species to select from t-test results
#' @param response_select Name of response to select from t-test results
#' @param data t-test results
#' @param p_check Boolean: should the p-value be required to be less than 0.05?
#'
#' @return A p-value for the selected species and response
ttest_pval <- function(species_select, response_select, data = t_test_results, p_check = TRUE) {
  data %>% 
    # Filter to appropriate species and response
    filter(species == species_select, response == response_select) %>%
    # Verify the p-value is significant (or override with `p_check = FALSE`)
    assert(function (x) magrittr::is_less_than(x, 0.05) | !p_check, p_value) %>%
    # Format the p-value
    mutate(
      p_value = case_when(
        p_value < 0.001 ~ "<0.001",
        TRUE ~ jntools::round_t(p_value, digits = 3))
    ) %>% 
    pull(p_value)
}
```

@@

Gametophytes of low elevation epiphytes had the highest DT (\circa{ }80% recovery), followed by high elevation epiphytes and saxicolous species (both with recovery from \circa{ }25% to 75%), with terrestrial species essentially non-tolerant (less than 20% recovery; Fig. 5).
<!-- FIXME: check on these numbers DT of gametophytes did not significantly exceed that of sporophytes for any species except for saxicolous *P. endlicherianum* (Fig. 5; *t*-test, *P* = `r ttest_pval("Polyphlebium_endlicherianum", "recovery")`), and was significantly lower in gametophytes than sporophytes of some high elevation epiphytic species including *C. minutum* var. 2, *H.* *digitatum*, *H. polyanthos*, and *P. borbonicum* (Fig. 5; *t*-test, *P* = `r ttest_pval("Crepidomanes_minutum2", "recovery")`, `r ttest_pval("Hymenophyllum_digitatum", "recovery")`, `r ttest_pval("Hymenophyllum_polyanthos", "recovery")`, and `r ttest_pval("Polyphlebium_borbonicum", "recovery")`, respectively). -->

@@

>>>>

```{r load-data}
tar_load(
  names = c(
    "refs",
    "refs_other",
    "climate",
    "filmy_species",
    "moorea_sites",
    "phylosig",
    "range_types",
    "combined_species_means",
    "t_test_results",
    "env_range_dt_model_summary"
  )
)
```

@@

# Make helper function to check on p-value significance and extract from t_test_results
#
#' @param species_select Name of species to select from t-test results
#' @param response_select Name of response to select from t-test results
#' @param data t-test results
#' @param p_check Boolean: should the p-value be required to be less than 0.05?
#'
#' @return A p-value for the selected species and response
ttest_pval <- function(species_select, response_select, data = t_test_results, p_check = TRUE) {
  data %>% 
    # Filter to appropriate species and response
    filter(species == species_select, response == response_select) %>%
    # Verify the p-value is significant (or override with `p_check = FALSE`)
    assert(function (x) magrittr::is_less_than(x, 0.05) | !p_check, p_value) %>%
    # Format the p-value
    mutate(
      p_value = case_when(
        p_value < 0.001 ~ "<0.001",
        TRUE ~ jntools::round_t(p_value, digits = 3))
    ) %>% 
    pull(p_value)
}

# FIXME: double check on these p-values
# ttest_pval("Polyphlebium_endlicherianum", "recovery")
# ttest_pval("Crepidomanes_minutum2", "recovery")
# ttest_pval("Hymenophyllum_digitatum", "recovery")
# ttest_pval("Hymenophyllum_polyanthos", "recovery")
# ttest_pval("Polyphlebium_borbonicum", "recovery")
```

@@

DT of gametophytes did not significantly exceed that of sporophytes for any species except for saxicolous *P. endlicherianum* (Fig. 5; *t*-test, *P* = ), and was significantly lower in gametophytes than sporophytes of some high elevation epiphytic species including *C. minutum* var. 2, *H.* *digitatum*, *H. polyanthos*, and *P. borbonicum* (Fig. 5; *t*-test, *P* = XXX, XXX, XXX, and XXX, respectively).

Gametophytes of low elevation epiphytes had the highest DT (\circa{ }80% recovery), followed by high elevation epiphytes and saxicolous species (both with recovery from \circa{ }25% to 75%), with terrestrial species essentially non-tolerant (less than 20% recovery; Fig. 5).

@@

## Figures
